Paper figures

### 2020-03-22 voltagebudget/analysis/paper_figures_lossy.Rmd
Unified facet box style

# Plot....
optimal_times %>% 
  ggplot(aes(x=ts*ms, y=ns)) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns, color=alg), 
               size=.6,
               alpha=0.8,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  geom_point(alpha=0.8, size=0.6) +
  facet_grid(alg~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  ggtitle("Optimal\ncompression") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

@@

# Figure 6 - osc freq v optimal
```{r, fig.width=2, fig.height=3, message=FALSE}
# Plot....
opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=0.6) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  facet_grid(freq~., labeller=hospital_labeller) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  labs(x="Compression (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  ggtitle("Optimal versus\nfrequency") +
  theme_classic() +
  theme(legend.position="right",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) -> p1

@@

# HERE - need to run sims to make the osc_times df
osc_times <- NULL
p3 <- osc_times %>% 
  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  facet_grid(.~As) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggtitle("Compression\nby oscillation")
p3 <- plot_spacer()

@@

# Figure 9 - trade-off (with osc)
```{r, message=FALSE, fig.width=3.8, fig.height=1.8}
vb_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(x=As, y=variances_pop*ms, color=As*1e9)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Peak amplitude (namps)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  theme_classic() + 
  theme(legend.position="none") -> p1

>>>>

# Plot....
optimal_times %>% 
  ggplot(aes(x=ts*ms, y=ns)) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns, color=alg), 
               size=.6,
               alpha=0.8,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  geom_point(alpha=0.8, size=0.6) +
  facet_grid(alg~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  ggtitle("Optimal\ncompression") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "grey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

@@

# Figure 6 - osc freq v optimal
```{r, fig.width=2, fig.height=3, message=FALSE}
# Plot....
opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=0.6) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  facet_grid(freq~., labeller=hospital_labeller) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  labs(x="Compression (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  ggtitle("Optimal versus\nfrequency") +
  theme_classic() +
  theme(legend.position="right",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.border = element_rect(fill = NA, colour = "grey"),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) -> p1

@@

# HERE - need to run sims to make the osc_times df
osc_times <- NULL
p3 <- osc_times %>% 
  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  facet_grid(.~As) +
  theme_classic() +
  theme(legend.position = "none",
        panel.border = element_rect(fill = NA, colour = "grey"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggtitle("Compression\nby oscillation")
p3 <- plot_spacer()

@@

# Figure 9 - trade-off (with osc)
```{r, message=FALSE, fig.width=3.6, fig.height=1.8}
vb_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(x=As, y=variances_pop*ms, color=As*1e9)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Peak amplitude (namps)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  theme_classic() + 
  theme(legend.position="none") -> p1
